Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-13 robdml.tex
pp2

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as Deep Metric Learning.
%
A well-designed loss function and a proper sampling method are crucial for DML
performance~\cite{dmlreality}.  As suggested by recent study, the classical
triplet loss could reach state-of-the-art performance with an appropriate
triplet sampling strategy~\cite{revisiting}.

@@

Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
$\va, \vp, \vn$, respectively.
%
Then the triplet loss~\cite{facenet} is defined as:
\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
%
\begin{equation}
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
	\end{equation}
%
%$
%
where $\gamma$ is a predefined margin parameter.
%
To attack the DML model, an imperceptible adversarial perturbation $\vr \in
\Gamma$ is added to the input image $\mX$, where $\Gamma = \{\vr | \mX+\vr\in
\mathcal{X},  \|\vr\|_p \leq \varepsilon\}$, so that its embedding vector
$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location towards
other positions to achieve the attacker's goal.
%
To defend against the attacks, the DML model can be adversarially trained to
reduce the effect of attacks~\cite{advrank,robrank}.
%
The most important metrics for a good defense is training cost, adversarial
robustness, and performance drop on benign examples.

>>>>

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as DML problem.
%
A well-designed loss function and a proper sampling method are crucial for DML
performance~\cite{dmlreality}.  For instance, the classical
triplet loss~\cite{facenet} could reach state-of-the-art performance with an appropriate
sampling strategy~\cite{revisiting}.

@@

Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
$\va, \vp, \vn$, respectively.
%
Then the triplet loss~\cite{facenet} is defined as:
%\setlength{\belowdisplayskip}{0pt} \setlength{\belowdisplayshortskip}{0pt}
%\setlength{\abovedisplayskip}{0pt} \setlength{\abovedisplayshortskip}{0pt}
%
\begin{equation}
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
	\end{equation}
%
%$
%
where $\gamma$ is a predefined margin parameter.
%
To attack the DML model, an imperceptible adversarial perturbation $\vr \in
\Gamma$ is added to the input image $\mX$, where $\Gamma = \{\vr | \mX+\vr\in
\mathcal{X},  \|\vr\|_p \leq \varepsilon\}$, so that its embedding vector
$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location towards
other positions to achieve the attacker's goal.
%
To defend against the attacks, the DML model can be adversarially trained to
reduce the effect of attacks~\cite{advrank,robrank}.
%
The most important metrics for a good defense is training cost, adversarial
robustness, and performance drop on benign examples.
